### 2022-06-23 README.Rmd
fix folder structure

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. Further, the analysis is divided into three 
    parts with different granularity/detail in time.
  - [:file\_folder: neo](/analysis/neo): Analysis for Neolithic B and C periods.
  - [:file\_folder: neo](/analysis/traditions): Analysis for pottery traditions.
  - [:file\_folder: neo](/analysis/groups): Analysis for pottery groups.
  - [:file\_folder: data](/analysis/data): Data used in the analysis. 
    We were not able to publish all our source data due to copyrights etc.
    There is also an individual data paper: <http://doi.org/10.5334/joad.88>.

>>>>

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. Further, the analysis is divided into three 
    parts with different granularity/detail in time.
  - [:file\_folder: neo](/analysis/neo): Analysis for Neolithic B and C periods.
  - [:file\_folder: traditions](/analysis/traditions): Analysis for pottery traditions.
  - [:file\_folder: groups](/analysis/groups): Analysis for pottery groups.
  - [:file\_folder: data](/analysis/data): Data used in the analysis. 
    We were not able to publish all our source data due to copyrights etc.
    There is also an individual data paper: <http://doi.org/10.5334/joad.88>.
